Toy Transit Surveys

### 2017-08-30 memos/workdir/toy_analytic_surveys.tex
update memo text

Write $\Gamma_{{\rm A,\ planets\ of\ }R_p} = \Gamma_{{\rm A,}R_p}$, 
and similarly for ${\rm D}$.
Just as in Model \#1, the answer to ``what is the relative difference between 
the occurrence rates derived by Astronomers D and A for planets of radius 
$R_p$?''
is simpler when we assume that Astronomer A has also derived a 
completeness, which we assume is the same as for Astronomer D in the single 
star case.
So Astronomer A now misclassifies planetary radii, and miscounts the total 
number of stars, but somehow knows his completeness for single 
stars. This is possible, because Astronomer A can correctly derive a 
completeness estimate and geometric transit probability for single stars only. 
For Astronomer $A'$ below, including the planets in binary star systems in the 
numerator actually introduces confusion that precludes nice math.
Then
\begin{equation}
	\Gamma_{{\rm A}, R_p} = \frac{N_{\rm det,s}/(f_{s,g} f_{s,c})}{N_s + N_d}.
\end{equation}

@@

In the limit where the $R_p$ planet has the same occurrence rate about every 
host type regardless of its mass, $\chi=2$, and this simplifies to $X_\Gamma = 
1+\beta$.
Although this is same expression as what we found for Model \#1, the value of 
$\beta$ will be smaller in this model because of the 
smaller volume of searchable binary stars.

If we consider the opposite limit of the $R_p$ planet \textit{only} 
existing around single stars and the primaries of double star systems with 
equal occurrence, $\chi = 1$, and $\Delta = \beta^2 / (1+2\beta)$.
For $\beta = 0.59$, this gives $\Delta = 0.16$.

@@

All of these diluted detections will be from binary systems. The number of 
planets detected in double star systems with observed radius $R_p^{\rm obs}$ 
is
\begin{align}
N_{\rm det,d}(R_p^{\rm obs}) &= N_{\rm det, d1}(R_p^{\rm obs}) + 
															  N_{\rm det, d2}(R_p^{\rm obs}) \\
&= \Gamma_{t,d1} f_{d1}(R_p^{\rm obs}) N_{d1}(R_p^{\rm obs})\  + \nonumber \\
&\quad\quad \quad\Gamma_{t,d2} f_{d2}(R_p^{\rm obs}) N_{d2}(R_p^{\rm obs}).
\end{align}
As always, the fractional terms $f_{di}$ for $i\in{1,2}$ encompass geometric 
and completeness corrections.
We're writing both them and the number of stars for which a given observed 
radius would be seen as functions of $R_p^{\rm obs}$.

@@

Then writing $N_{d1}(R_p')$, the number of double systems for which a $(R_p, 
P)$ planet would be observed in $R_p'$ if it orbiting the primary, is 
relatively straight-forward:
\begin{equation}
N_{d1}(R_p') = \int_{0}^{{\rm min}(1,\gamma_{R,u})} N_d(\gamma_R) 
\,{\rm prob}(\gamma_R) \,{\rm d}(\gamma_R),
\end{equation}
where the upper limit is set by equating the limiting radius $(1-x)R_p$ to the 
observed diluted radius $(1+\gamma_R)^{-1/2}R_p$, giving
\begin{equation}
\gamma_{R,u} \equiv \frac{x (2-x)}{(1-x)^2}.
\end{equation}
If $x > (1 - 2^{-1/2})$, bad things happen (cf. Fig.~\ref{fig:rad_vs_gammaR}), 
hence the need for the minimum.

The analogous equation for $N_{d1}(R_p')$, the number of double systems for 
which a $(R_p, P)$ planet would be observed in $R_p'$ if it orbiting the 
secondary, is
\begin{equation}
N_{d2}(R_p') = 
  \Bigg\{\begin{array}{lr}
  \int_{\gamma_{R,l}}^{1} N_d(\gamma_R)
  \,{\rm prob}(\gamma_R) \,{\rm d}(\gamma_R),\\ 
  \quad\quad\quad\quad\quad\quad\quad\quad x > 1 - 
  2^{-1/2}\\
  0, \quad\quad\quad\quad\quad\quad\quad x \leq 1 - 2^{-1/2}
  \end{array}
\label{eq:N_Rp_secondary}
\end{equation}
where
\begin{equation}
\gamma_{R,l} \equiv \frac{(1-x)^2}{x (2-x)}.
\end{equation}
Eq.~\ref{eq:N_Rp_secondary} accounts for the fact that you cannot measure 
$R_p$ to better than $\approx 29\%$ if the planet orbits the secondary of an 
unidentified binary.
This was originally noted in Fig.~\ref{fig:rad_vs_gammaR}.

If we were forward-modelling (\textit{i.e.} we actually wanted to compute 
$N_{\rm det,d}(R_p')$) we would need to evaluate the completeness 
term and this ``fraction of slightly diluted stars'' terms together, and 
integrate jointly to find $N_{\rm det,d1}(R_p')$ and $N_{\rm det,d2}(R_p')$.

\texttt{If we ask the right question, this will not be necessary.}

Astronomer A misclassifies planetary radii, miscounts the total number of 
stars, but knows his completeness and geometric correction for single stars as 
a function of radius $f_s(R_p')$.
His occurrence rate for planets of radius \textit{near} $R_p$, \textit{i.e.} 
the set of planets with $\{ (1-x)R_p < R_p^{\rm obs} < R_p \}$, is
\begin{equation}
\Gamma_{{\rm A}, R_p'} = \frac{ (N_{\rm det,s} + N_{\rm det,d}(R_p')) 
/ f_s(R_p')   }{ N_s + N_d}.
\end{equation}

For him,
\begin{equation}
f_s(R_p') = f_{s,g}(R_p') f_{s,c}(R_p').
\end{equation}

@@

>>>>

Write $\Gamma_{{\rm A,\ planets\ of\ }R_p} = \Gamma_{{\rm A,}R_p}$, 
and similarly for ${\rm D}$.
Just as in Model \#1, the answer to ``what is the relative difference between 
the occurrence rates derived by Astronomers D and A for planets of radius 
$R_p$?''
is simpler when we assume that Astronomer A has also derived a 
completeness, which we assume is the same as for Astronomer D in the single 
star case.
So Astronomer A now misclassifies planetary radii, and miscounts the total 
number of stars, but somehow knows his completeness for single 
stars. This is possible, because Astronomer A can correctly derive a 
completeness estimate and geometric transit probability for single stars only. 
For Astronomer $A'$ below, including the planets in binary star systems in the 
numerator introduces mistakes in the estimated completeness, and so the picture 
is more complicated.
Then
\begin{equation}
	\Gamma_{{\rm A}, R_p} = \frac{N_{\rm det,s}/(f_{s,g} f_{s,c})}{N_s + N_d}.
\end{equation}

@@

In the limit where the $R_p$ planet has the same occurrence rate about every 
host type regardless of its mass, $\chi=2$, and this simplifies to $X_\Gamma = 
1+\beta$.
This is same expression as what we found for Model \#1, but now the value of 
$\beta$ will be smaller in this model because of the 
smaller volume of searchable binary stars.
From numerics, we find $\beta = N_d/N_s = 0.59$, so the occurrence rate 
correction factor is $X_\Gamma(\chi=2) = 1.59$.

If we consider the opposite limit of the $R_p$ planet \textit{only} 
existing around single stars and the primaries of double star systems with 
equal occurrence, $\chi = 1$, and $X_\Gamma = (1 +\beta)^2 / (1+2\beta)$.
For $\beta = 0.59$, this gives $X_\Gamma(\chi=1) = 1.16$.
The true correction factor is somewhere between these two limits.

@@

The diluted detections only occur in binary systems. The number of 
planets detected in double star systems with observed radius $R_p^{\rm obs}$ 
is
\begin{align}
N_{\rm det,d}(R_p^{\rm obs}) &= N_{\rm det, d1}(R_p^{\rm obs}) + 
								N_{\rm det, d2}(R_p^{\rm obs}) \\
&= \Gamma_{t,d1} f_{d1}(R_p^{\rm obs}) N_{d1}(R_p^{\rm obs})\  + \nonumber \\
&\quad\quad \quad\Gamma_{t,d2} f_{d2}(R_p^{\rm obs}) N_{d2}(R_p^{\rm obs}).
\end{align}
As always, the fractional terms $f_{di}$ for $i\in{1,2}$ encompass geometric 
and completeness corrections.
We're writing both them and the number of stars for which a given observed 
radius would be seen as functions of $R_p^{\rm obs}$.

@@

Then writing $N_{d1}(R_p')$, the number of double systems for which a $(R_p, 
P)$ planet would be observed in $R_p'$ if it orbiting the primary, is 
relatively straight-forward:
\begin{equation}
N_{d1}(R_p') = \int_{0}^{{\rm min}(1,\gamma_{R,u})} N_d(\gamma_R) 
\,{\rm prob}(\gamma_R) \,{\rm d}(\gamma_R),
\label{eq:N_d1}
\end{equation}
where the upper limit is set by equating the limiting radius $(1-x)R_p$ to the 
observed diluted radius $(1+\gamma_R)^{-1/2}R_p$, giving
\begin{equation}
\gamma_{R,u} \equiv \frac{x (2-x)}{(1-x)^2}.
\end{equation}
If $x > (1 - 2^{-1/2})$, bad things happen (cf. Fig.~\ref{fig:rad_vs_gammaR}), 
hence the need for the minimum.
Note that Eq.~\ref{eq:N_d1} is not an expression for the number of detected 
planets about primaries -- that quantity is expressed as $\Gamma_{t,d1} 
f_{d1}(R_p^{\rm obs}) N_{d1}(R_p^{\rm obs})$.

The analogous equation to Eq.~\ref{eq:N_d1} for $N_{d2}(R_p')$, the number of 
double systems for which a $(R_p, P)$ planet would be observed in $R_p'$ if it 
orbited the secondary, is
\begin{equation}
N_{d2}(R_p') = 
  \Bigg\{\begin{array}{lr}
  \int_{\gamma_{R,l}}^{1} N_d(\gamma_R)
  \,{\rm prob}(\gamma_R) \,{\rm d}(\gamma_R),\\ 
  \quad\quad\quad\quad\quad\quad\quad\quad x > 1 - 
  2^{-1/2}\\
  0, \quad\quad\quad\quad\quad\quad\quad x \leq 1 - 2^{-1/2} % lol
  \end{array}
\label{eq:N_Rp_secondary}
\end{equation}
where
\begin{equation}
\gamma_{R,l} \equiv \frac{(1-x)^2}{x (2-x)}.
\end{equation}
Eq.~\ref{eq:N_Rp_secondary} accounts for the fact that you cannot measure 
$R_p$ to better than $\approx 29\%$ if the planet orbits the secondary of an 
unidentified binary.
This was originally noted in Fig.~\ref{fig:rad_vs_gammaR}.

If we were forward-modelling, \textit{i.e.} if we actually wanted to compute 
$N_{\rm det,d}(R_p')$, we would also need to evaluate the total detection 
efficiency term $f_{d1}(R_p^{\rm obs})$, which is a product of the geometric 
transit probability and the fraction of signals of a given depth that are 
detectable.
We would need to integrate this product over the domain of allowable radii 
$R_p'$ to find the number of detected planets.

However, the procedure of estimating the geometric transit probability, as well 
as the completeness, is complicated by the errors that are introduced by 
including binary star systems that are thought to be single in the numerator.
These stars will have incorrectly estimated masses and radii, which influences 
both $f_c(R_p')$ and $f_g(R_p')$.

\texttt{If we ask the right question, we will not need to actually compute 
either term.}

Astronomer A misclassifies planetary radii, miscounts the total number of 
stars, and (incorrectly) estimates his completeness and geometric correction 
for ``single'' stars as a function of radius $f(R_p')$ (omitting a ``s'' 
subscript because the stars for which this incorrect occurrence rate are 
derived are not all single).
His occurrence rate for planets of radius \textit{near} $R_p$, \textit{i.e.} 
the set of planets with $\{ (1-x)R_p < R_p^{\rm obs} < R_p \}$, is
\begin{equation}
\Gamma_{{\rm A}, R_p'} = \frac{ (N_{\rm det,s} + N_{\rm det,d}(R_p')) 
/ f_s(R_p')   }{ N_s + N_d}.
\end{equation}

For him,
\begin{equation}
f(R_p') = f_{g}(R_p') f_{c}(R_p').
\end{equation}

@@

%TODO: LEFT OFF HERE!
